---
title: "R Intro"
output: html_notebook
---

Loading libraries I'll need
```{r}
library(tidyverse)
```

Then my dataset and viewing it.
```{r}
library(readxl)

accidents_ke <- read_excel("C:/Users/Admin/Desktop/MY.123/Data Sets/kenya-accidents-database.xlsx")

accidents_ke

```

Getting a brief summary of the data set 

```{r}
glimpse(accidents_ke)
```
Removing the NO. and ...13 columns by their names
```{r}
droped <- accidents_ke %>% select( -NO., -...13)
droped
```

Next is to adjust the column names.

In this we first get the names of all our columns and their indexes:
```{r}
colnames(droped)
```
From there we have an option of chnaging the names either using the indexes or actual names:
```{r}
#Using the actual names

droped <- droped %>% rename(TIME ="TIME 24 HOURS"  )

droped <- droped %>% rename (BASES = "BASE/SUB BASE")
```

```{r}
#Using index
names(droped)[6] <- "DETAILS"
names(droped)[11] <- "YR-MM-DD"
```

Confirming whether the column names have chnaged:
```{r}
colnames(droped)
```

Removing duplicate observations based on the time and place columns
```{r}
droped %>% distinct(TIME, PLACE, .keep_all = TRUE)
```


